%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Konstantin Kotsev} % Your name
\address{Address: Ribaritsa 17, Sofia, Bulgaria} % Your address
\address{Mobile: 00359882525992 \\ konstantinkotsev@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Edinburgh} \hfill {\em June 2015} \\ 
BEng in Computer Science \\
First Class Honours

{\bf Sofia University} \hfill {\em September 2010 - June 2011} \\ 
BSc Software Engineering \\

\end{rSection}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Majio}{June 2014 - September 2014}{NLP Developer Internship}{Sofia, Bulgaria}
Researched and developed natural language processing (NLP) components of the system. Main tasks included: 
\item Prototyped initial GATE pipeline for rule based extraction of education information from CVs.
\item Researched and tested Name Entity Recognition components for the system to improve metrics on a corpus of test data.
\item Developed web scrapers in Python for extraction of data for NLP tasks.
\item Assisted with the curation of a corpus of annotated CVs and Job Offers.
\end{rSubsection}

\begin{rSubsection}{University of Edinburgh}{May 2015 - July 2015}{Research Assistant}{Edinburgh, United Kingdom}
\item Analyzed spacial temporal data in R and applied unsupervised machine learning to classify polluted areas in urban environments.
\item Developed a custom pollution visualization tool in R Shiny.
\item Curated and maintained a corpus of environmental data to be used in future analyses.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Science & Algorithms and Data Structures, Natural Language Processing \\
& Machine Learning, Probability Theory and Discrete Mathematics \\
Computer Languages & Java, Python, R, SQL, Hadoop \\
OS & Unix \\
Software Engineering & Object-oriented programming, Git \\
Technical Documentation & LaTeX

\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	RELEVANT PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}
\textbf{MyQoE}: Informatics Honours Project. This individual project involved elements of both practical experimentation for data gathering using a new sensor for pollution measurements, writing an Android App for data capture, and use of statistical/ML techniques for data analysis. A GitHub repository containing the collected corpus of data, code, and documentation was created for future students to reuse and quickly start work on the project. \\ \\
\textbf{System Design Project}: Worked as part of a team on prototyping an autonomous football robot using Java. Worked as part of the implementation team to develop the bluetooth communication system and the robot movement system. Created a unique movement system that allowed the robot to move efficiently in every direction. Participated in weekly performance reviews and conducted code reviews. \\ \\
\textbf{Time Table Application}: Developed an Android Application that would allow the user to quickly
access lecture schedule and view additional information about courses. \\ \\
\textbf{Fractal Flames Application}: Worked as part of a small team on developing a fractal generator in Java. The program won award for Best Graphical Application in the OOP course competition.
\end{rSection}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Languages}

English (Fluent) \\
Bulgarian (Native Speaker)

\end{rSection}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Interests}

I enjoy traveling to new countries and hiking in the mountains. In my free time I enjoy
doing sports and cooking.

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}